Blockchain System

### 2020-08-25 papers/execution-model/model.tex
rule1

\section{Rules}
\subsection{Transfers}
~\\
Rule 1 [proposal]:

\begin{equation}{}
\frac{\text{checkAcc($pkh$, \ACCOUNTS)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow \langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$)} ~\\\text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

>>>>

\section{Rules}
\subsection{Transfers}

Rule 1 [proposal]:

\begin{equation}{}
  \frac{
    \text{checkAcc($pkh$, \ACCOUNTS)}
  }{
    \parbox{4.5in}{\text{$\langle[\ACCOUNTS, \OPERATIONS,
        \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
        \TIME]\rangle \rightarrow$} \\
      \text{$\langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ)$ ::
        \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
        \CONTRACTORS, \TIME]$\rangle$}}}  
\end{equation}
~\\
~\\
Rule 2 [injected]:
